### 2019-01-15 tex/manuscript.tex
skeleton of tensile, fracture, and fatigue

	\section{Tensile testing and fracture mechanics} %shoot for 600 words
		Based on our understanding of the microstructure of the cuticle, it is possible to make several predictions about the mechanical behavior of the snout.
		First, we can predict that the endocuticle will contribute more to the tensile strength of the rostrum than the exocuticle, because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Second, the endocuticle will be less brittle than the exocuticle, therefore we should expect that fractures will initiate in the exocuticle.
		The predicted behavior of the snout is borne out by the data, where UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
		In addition to making the cuticle flexible, this profile makes it less likely to break, suggesting a possible means by which the system evolved (negative selection of breakage, maybe say this in conclusions).

		Outline:
		Intro
			To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the heads of 6 species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Tensile testing
			We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
			Consequently, there was a negative correlation between utlimate tensile strenth of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
			 All of these associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

			This strongly suggests that there is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology.

	\section{Fatigue testing of \textit{Curculio caryae}} %shot for 600 words

	\section{Conclusion} %shoot for 500 words

>>>>

	\section{Tensile testing of the rostrum} %shoot for 600 words
		To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the snouts of six species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Although the heads were rehydrated by immersion in de-ionized water for 24 hours, we observed comparatively brittle fracture (but see below), in contrast to GIVE EXAMPLES HERE.
		The tensile behavior for the cuticle of these weevils is a result of its microstructure, which lacks pores, etc (give reasons).
		THIS IS ALSO A GOOD SPOT TO SIGNPOST WHAT I FOUND IN GENERAL.

		\subsection{Tensile behavior}
			We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
			Consequently, there was a negative correlation between utlimate tensile strenth of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
			In other words, UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
			These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

			These data have three important implications:
			\begin{enumerate}
				\item There is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology. 
				\item The endocuticle contributes more to the tensile strength of the rostrum than the exocuticle, possibly because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
				\item Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes it less likely to break, suggesting a possible means by which the system evolved (via negative selection of breakage, maybe say this in conclusions).
			\end{enumerate}

			Finally, we observed that Young's modulus of elasticity is higher in specimens with a longer snout.
			This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
			Based on preliminary confocal microscopy data, we speculate that this phenomenon may be the result of a longer scrobe/transition/gradient from the basal profile to the apical profile in longer rostra.
			A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.
			[OR SAY MORE CONCISELY THAT: based on prelim CLSM data we believe that the snout is reinforced against bucking with thicker exocuticle in the base of these species; as a result, the higher volume fraction of exocuticle in the snout increases young's modulus for such species]

		\subsection{Fractography}
			Examination of the fracture surfaces and adjacent cuticle of tensile testing specimens revealed that although fracture was comparatively brittle, the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure, in agreement with previous studies (name some).

			In cross-section, the exocuticle consistently presented a smooth, nearly continuous fracture surface, indicative of relatively brittle fracture, likely due to the microarchitecture and resultant transverse isotropy of the Bouligand structure (explain this).
			Endocuticle, on the other hand exhibited severe delamination, ply-splitting, and fiber pulling, consistent with viscoelastic/plastic behavior shown in previous studies and congruent with theoretical consideration of the microstructure of this material (name something here). 
			These patterns indicate that the endocuticle is probably less brittle than the exocuticle, most likely due to the alignment of the $\alpha$-chitin fibers in each macrofiber.

			In addition, the exocuticle typically appears to fracture before the endocuticle, with shear-cusp formation evident over unbroken endocuticle.
			We note, however, that the exocuticle of weevils/beetles is anchored to the endocuticle by cross-linking fibers in a transition zone described by Kamp et al. (see refs.).
			The presence of shear-cusps therefore indicates that the fibers of the endocuticle are shearing past each other within each ply along the radial/normal plane (type II shearing???).
			Furthermore, given the delamination observed between plies, the layers of endocuticle are liekly shearing past each other (type III shearing) along the transverse plane.
			We therefore infer that, under tension, the endocuticle tends to deform visco-elastically and plastically along the longitudinal axes of the macrofibers, while the overlying exocuticle exhibits brittle fracture due to shearing between the stretching endocuticle fibers to which it is anchored.

			Additionally, the fracture surfaces show a characteristic failure mode, based on the pattern of fiber dislocation in the plies of the endocuticle.
			(copy description from DATA PRESENTATION, for figure 5B).

			From this pattern we hypothesize that the exocuticle-rich gular sutures are the most likely site for the initiation of void nucleation and failure of the integrated rostral cuticle in cross section.
			Structure failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
			We speculate that this could be the reason why the cross-sectional profile of \textit{C. caryae} is flattened ventrallyl
			Flattening this region may reduce tensile-strain across the gular sutures when the snout is bent dorsally, thus reducing the risk of fracture in the elongate, strongly-curved rostrum in this species.

	\section{Fatigue testing of \textit{Curculio caryae}} %shot for 600 words
		The shearing motion and accommodation of strain led us to question how the cuticle might accommodate repeated strain, as is seen in the living organism.
		We therefore performed fatigue testing on a female curculio longinasus, which exhibits the most extreme degree of bending in the sis species examined.

		~400K cycles, complete elongation, rehydrated, coated in grease to prevent loss of moisture and stiffening of the specimen.
		We observed visco-elastic behavior in the specimen, as indicated by histeresis in the stress-strain relationship during each cycle.
		Fmax decreased logarithmically with cycle number, etc., and the specimen appeared to have deformed plastically during the test.
		We initially believed that this indicated damage to the specimen; however, after cleaning the specimen in a 24 hour wash with ethanol and water, we observed that the specimen returned to its original shape.
		The specimen did not show any evidence of fractures or shear cusps anywhere in the surface of the exocuticle, and, furthermore, the tensile strength of the specimen was consistent with other members of its species.
		Given this surprising result, it appears that the specimen was undamaged by the testing.
		We therefore believe that under normal conditions in life, repeated bending of the snout does exceed the yield/plastic limit of the cuticle, and the bending strain is purely elastic/visco-elastic.

		We cannot fully account for these results, but we speculate that the microstructure of the endocuticle is resposible for what we observed.
		The endocuticle is made of aligned $\alpha$-chitin nanofibrils whose crystaline structure is enforced by hydrogen bonds between individual chitin chains along their length.
		The viscoelasticity of the cuticle is thought, in part, to come from slippage between these chains as the hydrogen bonds break and reform in response to shearing between the chitin molecules.
		We believe that repeated strain may have caused such slippage in the endocuticle of the rostral apex during the fatigue test, but without sufficient time for the material to \textit{completely} relax after deformation, the specimen would slowly accumulate strain and consequently deform visco-elastically/visco-plastically.
		After 24 hours soaking in ethanol and water, the hydrogen bonds would relax sufficiently to allow the specimen to return to its original configuration, dissipating the accumulated strain without any damage to the specimen.

	\section{Conclusions} %shoot for 500 words
